Estimating the number of migrants using between-population sibling pairs

### 2021-05-19 latex/ms.tex
add table

\articletype{Manuscript intended for \emph{Evolutionary Applications}, \today}%

@@

>>>>

\articletype{Manuscript intended for \emph{Methods in Ecology and Evolution}, \today}%

@@

\renewcommand{\arraystretch}{0.6}
\begin{table}[tb]
\begin{center}
   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
    \textbf {}\\[-4mm]
    \begin{tabular}{llc} \hline
       & & \\
	$n_{\rm M,1}, n_{\rm M, 2}$			& Sample number of parents in the subpopulation 1 and 2\\ 
		                						& \\
	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the subpopulation 1 and 2\\ 
		                						& \\
	$N_{1}, N_{2}$						& Number of parents in the subpopulation 1 and 2 when sampled\\
									& offspring are born\\
		                						& \\
	$M$								& Number of migrants of parents from the subpopulation 1 to the subpopulation 2\\
		                						& \\
	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
	                							& shares a mother-offspring relationship within the subpopulation 1 and 2\\
									& \\
	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
	                							& shares a mother-offspring relationship within the subpopulation 1 and 2\\
									& \\
	$\pi_{\rm MS}$			& Probability that a randomly selected pair (two offspring) \\
	                				& shares a maternal-sibling relationship\\
	$N_{\rm b,m}$			& Effective breeding number of mothers in the population\\
		                			& \\
	$\phi$		 		& Overdispersion parameter under negative binomial \\
						&reproduction\\
		                			& \\
	$\lambda_i$			& Expected number of surviving offspring of mother $i$\\
						& at sampling\\
		                			& \\	
	$f(\lambda)$			& Frequency of $\lambda$ for all mothers.\\
		                			& \\	
	$c$					& Combined effect of deviation from the Poisson \\
						&($=(1+\phi^{-1})\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$)\\
						& \\	
	$k_i$				& Number of surviving offspring born to mother $i$\\ 
	                				& \\
	$H_{\rm MO}$			& Number of mother--offspring pairs observed in samples\\ 
	                				& \\
	$H_{\rm MS}$			& Number of maternal-sibling pairs observed in samples\\ 
	                				& \\
	$\pi_{\rm MO}$			& Probability that a randomly selected pair (mother and offspring) \\
	                				& shares a mother-offspring relationship\\
						& \\
	$\pi_{\rm MS}$			& Probability that a randomly selected pair (two offspring) \\
	                				& shares a maternal-sibling relationship\\
						& \\
	$b$					& Bias of $\widehat{N_{\rm e,m}/N_{\rm m} }$\\
					        & & \\	                		
	\hline
    \end{tabular}
    \label{symbols} 
\end{center} 
\end{table}
\renewcommand{\arraystretch}{1}
